Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-16 ICML-submission/related-work.tex
thm 12 for randomized
Fix related work section

The problem of online bandit multiclass learning was initially formulated in the
pioneering work of~\citet{Auer-Long-1999}, under the name of ``weak reinforcement
model''. They showed that if all examples shown agrees with some
classifier in a prespecified hypothesis class $\calH$, then the optimal mistake
bound in the bandit setting can be upper bounded by the optimal mistake bound in
the full information setting, times a factor of $(2.01 + o(1))K \ln K$.
\citet{Long-2017} later improved the factor to $(1 + o(1)) K \ln K$ and showed its
 near-optimality.
\citet{Daniely-Helbertal-2013} extended the results to the setting where the
performance of the algorithm is measured by its regret, i.e. the difference
between the number of mistakes made by the algorithm and the number of mistakes
made by the best classifier in $\calH$ in hindsight. However, all algorithms
developed in this context are computationally inefficient.

@@

%Whether one can design an efficient algorithm with a finite mistake bound that
%has no dimensionality dependence is mentioned as an open problem in
%~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, where in this paper we provide a
%positive answer. $O(k^2 d \ln(\frac{d}{\gamma^2}))$
\chicheng{I significantly shortened the discussions of all those $\sqrt{T}$
regret algorithms here, as I think they are not very relevant.}

@@

%\citet{Abernethy-Rakhlin-2009} poses the open problem of
%whether one can design an efficient algorithm to get a $O(\sqrt{T})$ regret
%against some reasonable loss functions. \citet{Crammer-Gentile-2013} show that
%such an algorithm can be obtained, provided that the distribution of the label
%$y_t$ conditioned on feature vector $x_t$ satisfies certain parametric noise
%assumption. \citet{Hazan-Kale-2011} developed the \textsc{Newtron} algorithm,
%which has a regret between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass
%logistic loss, where the exact order of the regret depends on the diameter of
%the benchmark class. In particular, if the diameter is $O(\ln T)$, its regret
%bound would become $O(T^{2/3})$. The \textsc{SOBA} algorithm by
%\citet{Beygelzimer-Orabona-Zhang-2017} achieves a regret of
%$\widetilde{O}(\sqrt{T})$ against the
%$\eta$-loss~\citet{Orabona-Cesa-Bianchi-Gentile-2012}. In addition, its regret
%bound does not depend sensitively on the diameter of the benchmark class.
%\citet{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a
%regret of $\widetilde{O}(\sqrt{T})$ against the multiclass logistic loss, where
%it doubly-exponentially improves over \citet{Hazan-Kale-2011}'s regret on its
%dependence on the diameter of the benchmark class.

%\citet{Chen-Lin-Lu-2014}'s online weak learning condition implies that
%the set of examples is strongly separable by a convex combination of base
%hypotheses with a margin. Under this condition, it gives an algorithm with a
%$O(T^{3/4})$ mistake bound. \citet{Zhang-Jung-Tewari-2018} considers an online
%weak learning condition, which implies that all examples is separable by a
%convex combination of base hypotheses with a margin; see~\citet[Theorem
%3]{Mukherjee-Schapire-2013}. Under this condition, it gives a boosting algorithm
%with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge parameter. In
%addition, it gives an adaptive algorithm with a $O(T^{3/4})$ mistake bound.

%Online bandit multiclass learning is a special case of the contextual
%bandits problem~\citep{Auer-2003, Langford-Zhang-2008}, where the cost is the
%classification error. A series of works in the contextual bandits
%literature focuses on oracle-efficiency, that is, they assume access to an
%oracle that given a set of cost-sensitve learning examples, generates .

@@

%that receives a set of cost-sensitive learning
%examples and policy class $\Pi$,
%as algorithms generate cost-sensitive examples that may not be linearly
%separable Algorithms that satisfy oracle efficiency has been proposed in the
%literature, for example.

Recently, \citet{Foster-Krishnamurthy-2018} developed a rich theory of
contextual bandits with surrogate losses, focusing on regrets of the form
$\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{f \in \calF} \sum_{t=1}^T \frac{1}{K} \sum_{i=1}^K c_t(i) \phi( f_i(x_t)
)$, where $\calF$ contains score functions $f$ such that $\sum_{i=1}^K
f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac s \gamma, 0)$ or $\min(1,
\max(1 - \frac s \gamma, 0))$. On one hand, it gives information-theoretic
mistake upper bounds under various settings of $\calF$, including parametric and
nonparametric classes. On the other hand, it gives an efficient algorithm that
has a $O(\sqrt{T})$ regret against the benchmark of $\calF = \cbr{x \mapsto W x:
W \in \R^{k \times d}, \one^T W = 0}$. A direct application of this result to
online bandit multiclass linear classification yields an algorithm with a
$O(\sqrt{T})$ mistake bound in the strongly linearly separable setting.

>>>>

The problem of online bandit multiclass learning was initially formulated in the
pioneering work of~\citet{Auer-Long-1999}, under the name of ``weak
reinforcement model''. They showed that if all examples agree with some
classifier from a prespecified hypothesis class $\calH$, then the optimal
mistake bound in the bandit setting can be upper bounded by the optimal mistake
bound in the full information setting, times a factor of $(2.01 + o(1))K \ln K$.
\citet{Long-2017} later improved the factor to $(1 + o(1)) K \ln K$ and showed
its near-optimality. \citet{Daniely-Helbertal-2013} extended the results to the
setting where the performance of the algorithm is measured by its regret, i.e.
the difference between the number of mistakes made by the algorithm and the
number of mistakes made by the best classifier in $\calH$ in hindsight. However,
all algorithms developed in this context are computationally inefficient.

@@

%Whether one can design an efficient algorithm with a finite mistake bound that
%has no dimensionality dependence is mentioned as an open problem in
%~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, where in this paper we provide a
%positive answer. $O(k^2 d \ln(\frac{d}{\gamma^2}))$

@@

%\citet{Abernethy-Rakhlin-2009} poses the open problem of whether one can design
%an efficient algorithm to get a $O(\sqrt{T})$ regret against some reasonable
%loss functions. \citet{Crammer-Gentile-2013} show that such an algorithm can be
%obtained, provided that the distribution of the label $y_t$ conditioned on
%feature vector $x_t$ satisfies certain parametric noise assumption.
%\citet{Hazan-Kale-2011} developed the \textsc{Newtron} algorithm, which has a
%regret between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass logistic
%loss, where the exact order of the regret depends on the diameter of the
%benchmark class. In particular, if the diameter is $O(\ln T)$, its regret bound
%would become $O(T^{2/3})$. The \textsc{SOBA} algorithm by
%\citet{Beygelzimer-Orabona-Zhang-2017} achieves a regret of
%$\widetilde{O}(\sqrt{T})$ against the
%$\eta$-loss~\citet{Orabona-Cesa-Bianchi-Gentile-2012}. In addition, its regret
%bound does not depend sensitively on the diameter of the benchmark class.
%\citet{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a
%regret of $\widetilde{O}(\sqrt{T})$ against the multiclass logistic loss, where
%it doubly-exponentially improves over \citet{Hazan-Kale-2011}'s regret on its
%dependence on the diameter of the benchmark class.

%\citet{Chen-Lin-Lu-2014}'s online weak learning condition implies that the set
%of examples is strongly separable by a convex combination of base hypotheses
%with a margin. Under this condition, it gives an algorithm with a $O(T^{3/4})$
%mistake bound. \citet{Zhang-Jung-Tewari-2018} considers an online weak learning
%condition, which implies that all examples is separable by a convex combination
%of base hypotheses with a margin; see~\citet[Theorem
%3]{Mukherjee-Schapire-2013}. Under this condition, it gives a boosting
%algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge
%parameter. In addition, it gives an adaptive algorithm with a $O(T^{3/4})$
%mistake bound.

%Online bandit multiclass learning is a special case of the contextual bandits
%problem~\citep{Auer-2003, Langford-Zhang-2008}, where the cost is the
%classification error. A series of works in the contextual bandits literature
%focuses on oracle-efficiency, that is, they assume access to an oracle that
%given a set of cost-sensitve learning examples, generates .

@@

%that receives a set of cost-sensitive learning examples and policy class $\Pi$,
%as algorithms generate cost-sensitive examples that may not be linearly
%separable Algorithms that satisfy oracle efficiency has been proposed in the
%literature, for example.

Recently, \citet{Foster-Krishnamurthy-2018} developed a rich theory of
contextual bandits with surrogate losses, focusing on regrets of the form
$\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{f \in \calF} \sum_{t=1}^T \frac{1}{K}
\sum_{i=1}^K c_t(i) \phi( f_i(x_t) )$, where $\calF$ contains score functions
$f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac
s \gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
information-theoretic mistake upper bounds under various settings of $\calF$,
including parametric and nonparametric classes. On the other hand, it gives an
efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of
$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$. A direct
application of this result to \textsc{Online Bandit Multiclass Linear
Classification} yields an algorithm with a $O(\sqrt{T})$ mistake bound in the
strongly linearly separable setting.
